\section{Product Overview}

 {\pseProjectName} is a web-tool that enables its users to create, edit and manage machine learning \glslink{machine learning model}{model}s on different \gls{sensor} data. The web-tool consists of three primary components:

\begin{enumerate}
    \item \textbf{Desktop Web Client Application}
    The desktop web client application lets the clients create workspaces, manage their data and train/deploy \glslink{machine learning model}{model}s. Managing the data set includes creating new labels for the data and labeling the individual samples on an interactive graph.

    \item \textbf{Mobile Web Client Application}
    The mobile web client application lets the clients add new data samples or classify actions via the \gls{accelerometer} and \gls{gyroscope} \glspl{sensor} of their devices. For the data recording, the clients can choose a label for the recording, set a countdown duration before recording and set the recording duration. To classify an action, the clients perform the action and the classification happens in real time.

    \item \textbf{Server Application}
     Main functions of the server are handling the machine learning process (\gls{feature extraction} and preprocessing, \glslink{machine learning model}{model} training and deployment), data storage and serving the web clients, all of which are implemented independently from one another. These are then made available via a \gls{REST} API. 
     
\end{enumerate}

These components together allow for a streamlined and easy-to-use machine learning experience for the unexperienced and the expert.