\section{Purpose}
A web-tool that supports the entire machine learning process: from data collection to \glslink{machine learning model}{model} deployment.

\subsection{Core criteria}
\begin{itemize}
    \item The web pages are the \glspl{graphical user interface} (GUI) for users.
    \item Users register a new account or login with their existing accounts to use the tool. After logging in, the users are presented with their own set of \glslink{workspace}{workspaces} and a button to create a new \gls{workspace}.
    \item When creating a new \gls{workspace}, the user chooses a name for their new \gls{workspace}, the \glspl{sensor} that they wish to use in the \gls{workspace} and their sampling rate when recording samples and classifying actions. Supported \glspl{sensor} are \gls{accelerometer} and \gls{gyroscope}.
    \item The desktop client allows creating new labels and renaming the existing ones for the actions to be recorded in the \gls{workspace}. It also shows the amount of recorded samples with the label. 
    \item The desktop client presents a \gls{QR code} for data collection. The code connects the mobile client to the same \gls{workspace} when scanned. Each \gls{workspace} has its own unique \gls{QR code} for data collection and the recorded data is only visible to the \gls{workspace} that has served the \gls{QR code}.
    \item The mobile web client allows recording of \gls{data sample}s in form of raw \gls{sensor} data. The user chooses the \gls{label} for which they wish to record. Countdown and recording durations can be configured.
    \item The mobile web client gives a real time feedback of \gls{sensor} data to the user during the recording period.
    \item Recorded \gls{data sample}s are stored in a \gls{database} and displayed chronologically on the desktop web client. The user can view the \gls{metadata} of the sample by clicking on it. The user can also view the data as a time graph on which they can \gls{label} the relevant time frames. The user can remove or relabel samples.
    \item The desktop web client presents the user \gls{feature extraction} and feature preprocessing options.\footnote{\label{exact}Exact details can be found in the functional requirements}
    \item The desktop web client allows training a \glslink{machine learning model}{model} with the selected learning method, the selected options and the data set of the \gls{workspace}.\textsuperscript{\ref{exact}}
    \item Trained and available \glslink{machine learning model}{model}s of the current \gls{workspace} are listed on the desktop web client. The user can view the \gls{metadata} of each \glslink{machine learning model}{model}, e.g. parameters and \glspl{data sample} used for the training or performance metrics by clicking on the \glslink{machine learning model}{model}.\textsuperscript{\ref{exact}}
    \item Each \glslink{machine learning model}{model} in a \gls{workspace} is assigned a link which the user can use on a mobile device to classify action with the respective \glslink{machine learning model}{model}. This \gls{classification} happens in real time. The user can view the link as well as the \gls{QR code} with the same link embedded to ease usage. 
    \item User can stop the \gls{classification} at any time to view the classified actions. They can later resume the \gls{classification}.   
\end{itemize}

\subsection{Optional criteria}
\begin{itemize}
    \item The desktop web client serves a "Stay Signed In" functionality.
    \item The desktop web client displays a status sign if a data collecting device is currently connected to the \gls{workspace}, e.g. a green sign if connected and a red sign otherwise.
    \item The mobile web client can define triggers if something is detected, e.g. play a sound.
    \item Workspaces can be deleted together with the related \glspl{data sample}.
    \item \Glspl{data sample} can be transferred between compatible \glspl{workspace}.
    \item Labels will have a description that can be edited on how the action has to be performed. This description will be shown on the mobile client when a data with that \gls{label} is recorded.
    \item A single \gls{workspace} can be shared among several accounts.
    \item The \glslink{graphical user interface}{GUI} can support several languagues.
    \item Other \glspl{sensor} can also be supported.
    \item "Forgot password" option is presented to user on the desktop web client to recover credentials.
    \item A \gls{CAPTCHA} technology is implemented to prevent brute force attacks.
\end{itemize}

\subsection{Exclusion criteria}
\begin{itemize}
    \item The mobile web client does not implement a \gls{QR code} scanner.
    \item The user cannot change the \glspl{sensor} used in a \gls{workspace}.
    \item Each web page is designed for either a desktop device or a mobile device.
    \item Trying to display a web page in an unsupported device shows an error to the client.
\end{itemize}
